---
title: "WORKSHEET 5"
author: "ELMAR AUGUSTINE FERNANDEZ"
date: "2022-11-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
#Course Year 2019 - 2020
#  1st           80
#  2nd           75
#  3rd           70
#  4th           60

#a. Plot the data using a bar graph. Write the codes and copy the result.
```{r}
x2019_2020 <- c(80,75,70,60)
numb_1a <- barplot(x2019_2020)
```


#b. Using the same table, label the barchart with
#Title = ” Enrollment of BS Computer Science
#horizontal axis = “Curriculum Year” and
#vertical axis = “number of students”
```{r}
course <- c("1st","2nd","3rd","4th")

numb_1b <- barplot(x2019_2020,
                   main = "Enrollment of BS Computer Science",
                   xlab = "Curriculum Year", names.arg = course)
```

#2. The monthly income of De Jesus family was spent on the following:

#60% on Food, 10% on electricity, 5% for savings, and
#25% for other miscellaneous expenses.


#a. Create a table for the above scenario.


#Write the codes and its result.
```{r}
expenses <- c(60,10,5,25)
barplot(expenses,names.arg = c("Food", "Electricity", "Savings", "Miscllaneous"))
```


#b. Plot the data using a pie chart. Add labels, colors and legend.

#Write the codes and its result.
```{r}
pie(expenses)
num <- pie(expenses,
              col =rainbow (length(expenses)),
              labels = c(60,10,5,25))

ex_labels <- round(expenses/sum(expenses) * 100, 1)

ex_labels <- paste(ex_labels,"%",sep = "")
pie(expenses, main = "Expenses",col= rainbow (length(expenses)),labels = ex_labels,cex=0.8)

legend(1, c("Food", "Electricity", "Savings", "Miscllaneous"),
       cex = 0.8,fill = rainbow((length(expenses))))
```

#3. Open the mtcars dataset.
```{r}
data("mtcars")
num3 <- mtcars$mpg
num3
```


#a. Create a simple histogram specifically for mpg (miles per gallon) variable.
#Use $ to select the mpg only. Write the codes and its result.
```{r}
num3a <-hist(num3, xlab="Miles Per Gallon",
              main="Histogram of mpg")
```



#b. Colored histogram with different number of bins.
```{r}
num3b <-hist(num3, breaks=12, col="yellow", xlab="Miles Per Gallon",
              main="Histogram of mpg")
```

#Note: breaks= controls the number of bins

#c. Add a Normal Curve
```{r}
num3c <-hist(num3, breaks=12, col="pink", xlab="Miles Per Gallon",
              main="Histogram with Normal Curve")
xfit<-seq(min(num3),max(num3),length=40)
yfit<-dnorm(xfit,mean=mean(num3),sd=sd(num3))
yfit <- yfit*diff(num3c$mids[1:2])*length(num3)
lines(xfit, yfit, col="orange", lwd=2)
```



#Copy the result.


#4. Open the iris dataset. Create a subset for each species.

#a. Write the codes and its result.
```{r}
data("iris")
setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")
```


#b. Get the mean for every characteristics of each species using colMeans().
#Write the codes and its result.
```{r}
set <- subset(iris, Species == "setosa")
setosa <- colMeans(set[sapply(set,is.numeric)])
setosa
```
```{r}
ver <- subset(iris, Species == "versicolor")
versicolor <- colMeans(ver[sapply(ver,is.numeric)])
versicolor

```
```{r}
vir <- subset(iris, Species == "virginica")
virginica <- colMeans(vir[sapply(vir,is.numeric)])
virginica
```




#Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
#c. Combine all species by using rbind()
#The table should be look like this:
```{r}
tran8 <- rbind(setosa,
                versicolor,
                virginica)
tran8
```

#Sepal.Length Sepal.Width Petal.Length Petal.Width
#setosa
#versicolor
#virginica


#d. From the data in 4-c: Create the barplot().
#Write the codes and its result.
#The barplot should be like this.
```{r}
barplot(tran8, beside = TRUE,
        main = "Iris Mean",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("pink","orange","violet")) 
```

#Figure 1: Iris Data using Barplot
