---
title: "INDIVIDUAL PROJECT 2"
author: "ELMAR AUGUSTINE FERNANDEZ"
date: "2022-12-10"
output: html_document
---

```{r}
library(wordcloud)
library(plotly)
library(tm)
library(dplyr)
library(RColorBrewer)
library(ggplot2)
library(twitteR)
```


# SETUP CREDENTIALS.
```{r}
CONSUMER_KEY <- "7KrD22KUMcdamkdHgR3WOA2QP"
CONSUMER_SECRET <- "hGbT8EMCtDRvK79NXHTteGl1YvIz9xenZX8qvWjN8SAIKCO7nD"
ACCESS_TOKEN <-  "1596512522408202240-kEkdMunH6t5SpjneM0fjsUURFvlY0c"
ACCESS_SECRET <-  "U7h5Y2P8JyblzoxX6Zc0hzK5tQpMYYGj6iesEzMU0P54z"
```


#Connect to twitter app.
```{r}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)

```

# EXTRACTING TWEETS.
```{r}
Footballtweets <- searchTwitter("#Messi", n=10000, lang="en", since="2022-11-25", until="2022-12-08", retryOnRateLimit = 120)
Footballtweets
```


# CONVERTING LIST DATA TO DATA FRAME.
```{r}
FootballtweetsDF <- twListToDF(Footballtweets)
```


# SAVE DATA FRAME FILE.
```{r}
save(FootballtweetsDF,file = "FootballTweetsDF.Rdata")
```


# LOAD DATA FRAME FILE.
```{r}
load(file = "FootballTweetsDF.Rdata")
```


# CHECKING FOR MISSING VALUES IN A DATA FRAME.
```{r}
sap_data <- sapply(FootballtweetsDF, function(x) sum(is.na(x)))
sap_data
```


#Tweets
# SUBSETTING USING THE dplyr() PACKAGE.
```{r}
tweets <- FootballtweetsDF %>%
  select(screenName,text,created, isRetweet) %>% filter(isRetweet == FALSE)
tweets
```


# GROUPING THE DATA CREATED. 
```{r}
tweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

crt_data <- tweets %>%  mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
crt_data

mn <- tweets %>% pull(created) %>% min()
mn 
mx <- tweets %>% pull(created) %>% max()
mx
```


# Plot on tweets by time using the library(plotly) and ggplot().
```{r}
plt_data <- ggplot(crt_data, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "green", high = "yellow")

plt_data %>% ggplotly()

```

#Retweets

```{r}
sub_tweets <- FootballtweetsDF %>%
  select(screenName,text,created, isRetweet) %>% filter(isRetweet == TRUE)
sub_tweets


sub_tweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

crt2 <- sub_tweets %>%  mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
crt2

mn <- sub_tweets %>% pull(created) %>% min()
mn 
mx <- sub_tweets %>% pull(created) %>% max()
mx
```


# Plot on tweets by time using the library(plotly) and ggplot().
```{r}
plt_data <- ggplot(crt2, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "green", high = "yellow")

plt_data %>% ggplotly()
```

